Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-06-25 PAPER/main.tex
put heuristics into paragraphs

\subsection{Modified First-Fit Decreasing Heuristic (MFFD)}
\label{sec:mffd}
The \textsc{Modified First-Fit Decreasing} (MFFD) heuristic performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip. If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item. If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, else the heuristic attempts to pack the item onto the next lowest-indexed strip. For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled in either orientation of the item, and therefore it cannot be feasibly packed onto the strip.

@@

\subsection{Pair-Smallest Heuristic (PS)}
\label{sec:ps}

The \textsc{Pair-Smallest} (PS) heuristic is an extension of a procedure defined by \cite{lewis2011}. Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any more items feasibly. Each strip is initialised by choosing the item from $\mathcal{I}$ with the smallest score width, and packing it in a regular orientation. PS then continues to fill the strip by selecting the item with the smallest score width that meets the vicinal sum constraint with the right-most score width on the strip, and whose width will not cause the strip to be overfilled. This heuristic aligns the smallest score widths with the largest ones, eliminating the possibility of placing larger score widths together unecessarily. Note that PS prioritises the vicinal sum constraint over the item widths, choosing to fulfil the constraint first before considering whether the item can be accommodated. If there are multiple items with equal score widths, break ties by choosing the item whose second score width is the largest.
% Break ties by choosing item whose second score width is larger.
% If item with smallest feasible score width does not fit onto the strip, choose item with next smallest score width and repeat.

\subsection{Modified First-Fit Decreasing with AHC (MFFD$^+$)}
\label{sec:mffd+}

The last heuristic incorporates AHC as described in Section \ref{sec:ahca}. The \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip. However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}). If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip. Using AHC means that if a feasible alignment of the items exists, there is a guarantee that it will be found. Unlike MFFD, where the current item can only be placed on the end of the strip, MFFD$^+$ allows the items to be entirely rearranged (see Figure \ref{fig:comparestrips}). This reduces the possibility of having to start a new strip for an item, thus preventing increasing the number of strips in the final solution. Since AHC is executed every time an item can fit onto a strip that already contains items, (up to $|\mathcal{S}|$ times per item, where $|\mathcal{S}|$ is the number of strips containing at least one item so far in the procedure) MFFD$^+$ is slower in comparison to the previous heuristics.

>>>>

The first heuristic we developed is the \textsc{Modified First-Fit Decreasing} (MFFD) heuristic which performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip. If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item. If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, else the heuristic attempts to pack the item onto the next lowest-indexed strip. For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled in either orientation of the item, and therefore it cannot be feasibly packed onto the strip.

@@

The next heuristic is the \textsc{Pair-Smallest} (PS) heuristic, an extension of a procedure defined by \cite{lewis2011}. Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any more items feasibly. Each strip is initialised by choosing the item from $\mathcal{I}$ with the smallest score width, and packing it in a regular orientation. PS then continues to fill the strip by selecting the item with the smallest score width that meets the vicinal sum constraint with the right-most score width on the strip, and whose width will not cause the strip to be overfilled. This heuristic aligns the smallest score widths with the largest ones, eliminating the possibility of placing larger score widths together unecessarily. Note that PS prioritises the vicinal sum constraint over the item widths, choosing to fulfil the constraint first before considering whether the item can be accommodated.
%If there are multiple items with equal score widths, break ties by choosing the item whose second score width is the largest.
% If item with smallest feasible score width does not fit onto the strip, choose item with next smallest score width and repeat.

The last heuristic, \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$), incorporates AHC as described in Section \ref{sec:ahca}. MFFD$^+$ operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip. However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}). If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip. Using AHC means that if a feasible alignment of the items exists, there is a guarantee that it will be found. Unlike MFFD, where the current item can only be placed on the end of the strip, MFFD$^+$ allows the items to be entirely rearranged (see Figure \ref{fig:comparestrips}). This reduces the possibility of having to start a new strip for an item, thus preventing increasing the number of strips in the final solution. 
%Since AHC is executed every time an item can fit onto a strip that already contains items, (up to $|\mathcal{S}|$ times per item, where $|\mathcal{S}|$ is the number of strips containing at least one item so far in the procedure) MFFD$^+$ is slower in comparison to the previous heuristics.
